Clustering time series based on probability distributions across temporal granularities

### 2021-11-11 main.Rmd
sindex plot added

@@

>>>>

- sindex is plotted against the number of clusters ($k$) in Figure \ref{fig:cluster-number-selection-validation}. This can be used to determine the number of clusters for each scenario. Each line in the plots represents a different simulation setting for the same scenario. When sindex for each scenario are examined, it appears that $k = 5, 4, 4$ is justified for scenarios S1, S2, and S3, respectively, given the sharp decrease in sindex from that value of $k$. The number of clusters corresponds to the number of designs that were originally considered in each scenario.

@@

```{r cluster-number-selection-validation, fig.cap="sindex plotted as a function of the number of clusters for S1, S2, and S3. S1 has a sharp decrease in sindex from 5 to 6, whereas S2 and S3 have a decrease from 4 to 5. As a result, the number of clusters considered for S1, S2, and S3 is 5, 4, 4, respectively. This corresponds to the number of designs taken into account in each scenario."}
```
